Summary of tumor cell classification with `AUCell` for `r params$library_id`

### 2024-07-11 analyses/cell-type-ewings/template_notebooks/auc-workflow/01-auc-results.Rmd
go back to null variables

---
title: "Summary of tumor cell classification with `AUCell` for `r params$library_id`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  library_id: SCPCS000490
  sce_file: "../../../../data/current/SCPCP000015/SCPCS000490/SCPCL000822_processed.rds"
  aucell_results_file: "../../results/aucell_annotation_test/SCPCS000490/SCPCL000822_auc-classifications.tsv"
  ref_auc_results: "../../results/aucell_annotation_test/SCPCS000490/SCPCL000822_auc-classifications.tsv"
  geneset_scores_file: "../../results/aucell_annotation_test/SCPCS000490/SCPCL000822_gene-set-scores.tsv"
  marker_genes_file: "../../references/tumor-marker-genes.tsv"
  auc_threshold: 0.009131468
---

>>>>

---
title: "Summary of tumor cell classification with `AUCell` for `r params$library_id`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  library_id: NULL
  sce_file: NULL
  aucell_results_file: NULL
  ref_auc_results: NULL
  geneset_scores_file: NULL
  marker_genes_file: NULL
  auc_threshold: NULL
---
